WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-07-19 article/Article.tex
use \part to be able to use more subsections
darcs-hash:20060719131744-2fc9d-4d1b52fe1552ba4f02347a505fd7bfbf98feeeb8.gz

\section{Introduction}

@@

\section{Supported languages and plateforms}

@@

\section{Performance}

\section{User guide}

  \subsection{Installation}

    \subsubsection{Get the software sources}

@@

    \subsubsection{ITK}

@@

    \subsubsection{CableSwig}

@@

    \subsubsection{Python}

@@

    \subsubsection{Tcl}

@@

    \subsubsection{Java}

@@

    \subsubsection{Build options}

@@

    \subsubsection{Install WrapITK or use it in the build tree}

@@

    \subsubsection{Binary packages}

@@

  \subsection{Python usage}

@@

     \subsubsection{Configuring python and importing the libraries}

@@

     \subsubsection{Template usage}
Most class in the itk python module are "template proxy classes" that
encapsulate all of the template instantiations that were created at build time.
If three-dimensional \verb$unsigned char$ and \verb$unsigned short$ image types were created,
they can be accessed as follows:
\begin{itemize}
  \item \verb$itk.Image[itk.UC, 3]$
  \item \verb$itk.Image[itk.US, 3]$
\end{itemize}
Note that the C type \verb$unsigned char$ is given with \verb$itk.UC$, and \verb$unsigned short$
with \verb$itk.US$.

@@

     \subsubsection{The {\em New()} method}

@@

     \subsubsection{Python sequences and ITK}

@@

     \subsubsection{Python specific functions in the {\em itk} module}

@@

     \subsubsection{Advanced Features}

@@

     \subsubsection{Full python script examples}

@@

    \subsection{TCL usage}

@@

    \subsection{Java usage}

@@

\section{Developer guide}

@@

  \subsection{WrapITK description}

     \subsubsection{Creating a CMakeLists.txt file for a wrapper library}
Each WrapITK sub-library (e.g. \verb$Base$, or \verb$SpatialObject$) lives in a
sub-directory of the WrapITK project (within the \verb$Modules$ directory) with a
\verb$CMakeLists.txt$ file that describes how that library  and language support files
(e.g. python template definitions) is to be created. Moreover, any external
project will need a similar file to describe how to create that library.

@@

     \subsubsection{Creating wrap\_XXX.cmake files to wrap classes}

@@

  \subsection{Extending or customizing WrapITK}

@@

  \subsection{External projects}

    \subsubsection{Why external projects?}

@@

    \subsubsection{Building}
To build an external project, first ensure that WrapITK has been properly built.
Then use \verb$ccmake$ to configure a build directory for the external project. If
WrapITK has not been installed, you will have to manually enter the path to the
WrapITK build directory.

@@

    \subsubsection{Usage}
Once an external project has been built, it can be tested directly from the
build tree. Start python in the external project build directory's Python
subdirectory, and run the command \verb$import ProjectConfig$ (or 
\verb$import ProjectConfig-[Debug|Release|...]$ if you were using an IDE, depending on which
build configuration was set from the IDE). This command sets up the search paths
properly so that WrapITK and the newly-created library files can be found. Then
type \verb$import ...$ (where \verb$...$ is replaced with the name of the external
project; e.g. \verb$import BufferConversion$), and use the project.

    \subsubsection{Installation}
Simply type \verb$make install$ (or run your IDE's install step) to install the
external project into the WrapITK tree (provided WrapITK has already been
installed). Now the external project can be used just like any of the other
WrapITK libraries, and it will be imported into the \verb$itk$ namespace when the
\verb$import itk$ command is issued from Python.

    \subsubsection{Top-level CMakeLists for external projects}
In addition to having a set of \verb$wrap_XXX.cmake$ files and the proper
commands to read in these files and create a library (all described above), an
external project's CMakeLists file needs at least one additional command to
start it out: \verb$FIND_PACKAGE(WrapITK REQUIRED)$.

@@

    \subsubsection{Examples}

@@

    \subsubsection{BufferConversion: an example of extension for one language}

@@

    \subsubsection{ItkVtkGlue: an example of extension for all languages, including C++}

@@

  \subsection{Extending language support and adding more languages}

@@

    \subsubsection{Generating target language code}

@@

    \subsubsection{typemaps}

@@

  \subsection{Contributing to WrapITK}
\label{section:contribute}

@@

\section{Acknowledgments}
I thank Dr Pierre Adenot and all the {\em Embryon et Biotechnologie} team for their
patience during the long development time before getting a tool really usable.

@@

\section{Conclusion}

@@

\appendix

>>>>

\newpage
\part{Introduction}

@@

\newpage
\part{Supported languages and plateforms}

@@

\newpage
\part{Performance}

\newpage
\part{User guide}

  \section{Installation}

    \subsection{Get the software sources}

@@

    \subsection{ITK}

@@

    \subsection{CableSwig}

@@

    \subsection{Python}

@@

    \subsection{Tcl}

@@

    \subsection{Java}

@@

    \subsection{Build options}

@@

    \subsection{Install WrapITK or use it in the build tree}

@@

    \subsection{Binary packages}

@@

  \section{Python usage}

@@

     \subsection{Configuring python and importing the libraries}

@@

     \subsection{Template usage}
Most class in the itk python module are "template proxy classes" that
encapsulate all of the template instantiations that were created at build time.
If three-dimensional \verb$unsigned char$ and \verb$unsigned short$ image types were created,
they can be accessed as follows:
\begin{itemize}
  \item \verb$itk.Image[itk.UC, 3]$
  \item \verb$itk.Image[itk.US, 3]$
\end{itemize}
Note that the C type \verb$unsigned char$ is given with \verb$itk.UC$, and \verb$unsigned short$
with \verb$itk.US$.

@@

     \subsection{The {\em New()} method}

@@

     \subsection{Python sequences and ITK}

@@

     \subsection{Python specific functions in the {\em itk} module}

@@

     \subsection{Advanced Features}

@@

     \subsection{Full python script examples}

@@

    \section{TCL usage}

@@

    \section{Java usage}

@@

\newpage
\part{Developer guide}

@@

  \section{WrapITK description}

     \subsection{Creating a CMakeLists.txt file for a wrapper library}
Each WrapITK sub-library (e.g. \verb$Base$, or \verb$SpatialObject$) lives in a
sub-directory of the WrapITK project (within the \verb$Modules$ directory) with a
\verb$CMakeLists.txt$ file that describes how that library  and language support files
(e.g. python template definitions) is to be created. Moreover, any external
project will need a similar file to describe how to create that library.

@@

     \subsection{Creating wrap\_XXX.cmake files to wrap classes}

@@

  \section{Extending or customizing WrapITK}

@@

  \section{External projects}

    \subsection{Why external projects?}

@@

    \subsection{Building}
To build an external project, first ensure that WrapITK has been properly built.
Then use \verb$ccmake$ to configure a build directory for the external project. If
WrapITK has not been installed, you will have to manually enter the path to the
WrapITK build directory.

@@

    \subsection{Usage}
Once an external project has been built, it can be tested directly from the
build tree. Start python in the external project build directory's Python
subdirectory, and run the command \verb$import ProjectConfig$ (or 
\verb$import ProjectConfig-[Debug|Release|...]$ if you were using an IDE, depending on which
build configuration was set from the IDE). This command sets up the search paths
properly so that WrapITK and the newly-created library files can be found. Then
type \verb$import ...$ (where \verb$...$ is replaced with the name of the external
project; e.g. \verb$import BufferConversion$), and use the project.

    \subsection{Installation}
Simply type \verb$make install$ (or run your IDE's install step) to install the
external project into the WrapITK tree (provided WrapITK has already been
installed). Now the external project can be used just like any of the other
WrapITK libraries, and it will be imported into the \verb$itk$ namespace when the
\verb$import itk$ command is issued from Python.

    \subsection{Top-level CMakeLists for external projects}
In addition to having a set of \verb$wrap_XXX.cmake$ files and the proper
commands to read in these files and create a library (all described above), an
external project's CMakeLists file needs at least one additional command to
start it out: \verb$FIND_PACKAGE(WrapITK REQUIRED)$.

@@

    \subsection{Examples}

@@

    \subsection{BufferConversion: an example of extension for one language}

@@

    \subsection{ItkVtkGlue: an example of extension for all languages, including C++}

@@

  \section{Extending language support and adding more languages}

@@

    \subsection{Generating target language code}

@@

    \subsection{typemaps}

@@

  \section{Contributing to WrapITK}
\label{section:contribute}

@@

\newpage
\part{Acknowledgments}
I thank Dr Pierre Adenot and all the {\em Embryon et Biotechnologie} team for their
patience during the long development time before getting a tool really usable.

@@

\newpage
\part{Conclusion}

@@

\newpage
\appendix
